---
title: "demog_bhv.rmd"
author: "chrysie"
date: "2024-10-18"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

### packages and libraries
```{r}
install.packages("pastecs")
library(pastecs)
```

```{r loading the data}
db_data <- read.csv("../data/ca_demog_bhv.csv")
```

### the data
-   **ID**

    -   **ANH000 - autims-anxiety controls**

    -   **AC000 - autism controls**

    -   **AN000 - autism and anxiety**

    -   **RDH000 - disruptive behaviour-irritability controls**

    -   **RD000 - disruptive behaviour and irritability (some with
        ASD)**

-   **IQ**

-   **IQ_demeaned - IQ scores centered**

-   **Age**

-   **Age_demeaned - age centered**

-   **Gender**

    -   **1 - male**

    -   **0 - female**

-   **Race**

    -   **2**

    -   **4**

    -   **5**

    -   **6**

-   **Ethnicity** - Hispanic or not

    -   1

    -   0

-   **Meds**

    -   **1 - yes, on medication**

    -   **0 - no, not on medication**

-   **Baseline_fdmean** - baseline framewise displacement mean

-   **Include_lowmotion**

    -   **1 - yes, ppt had low motion**

    -   **0 - no, ppt had high motion**

-   **Motioncutoff0.5**

    -   1 - below 0.5 motion

    -   0 - above 0.5 motion

-   **SRS_SCI_Tscore** - social responsiveness scale social
    communication index t scores

-   **SRS_SCI** - social responsiveness scale social communication index
    raw scores

-   **SCI_demeaned** - SRS social communication index raw scores
    centered

-   **SRS_RRB_Tscore** - social responsiveness scale restricted
    repetitive behaviours t scores

-   **SRS_RRB** - social responsiveness scale restricted repetitive
    behaviours raw scores

-   **RRB_demeaned** - SRS restricted repetitive behaviour raw scores
    centred

-   **SRS_TOTAL_Tscore** - social responsiveness scale total t scores

-   **SRS_total** - social responsiveness scale total raw scores

-   **SRS_demeaned** - SRS raw scores centered

-   **MASC(PV)** - multidimensional anxiety scale for children scores

### descriptive stats
```{r}
desc_stats <- pastecs::stat.desc(db_data, basic=FALSE, norm=TRUE)

```


